Containers and R: the Rockerverse and beyond

### 2019-08-12 manuscript.Rmd
Rough bioc brainstroming session for rockerverse paper.
- This session included @lshep and @nturaga

- Jot down all the points which might be relevant.

- Next sessions include, arrange , clean up and write

- [MRO](https://github.com/nuest/mro-docker)
- [Renjin](https://github.com/nuest/renjin-docker)
- [pqR](https://github.com/nuest/pqr-docker)
- [FastR](https://github.com/nuest/fastr-docker)
- [Bioconductor](http://bioconductor.org/help/docker/), https://github.com/Bioconductor/bioc_docker

>>>>

- [MRO](https://github.com/nuest/mro-docker)
- [Renjin](https://github.com/nuest/renjin-docker)
- [pqR](https://github.com/nuest/pqr-docker)
- [FastR](https://github.com/nuest/fastr-docker)

- [Bioconductor](http://bioconductor.org/help/docker/), https://github.com/Bioconductor/bioc_docker

- Most system dependencies come from rocker/r-ver and rocker/rstudio
  as needed.

- Bioconductor works on two release cycles every year.

- Docker images based on rocker/rstudio for release and devel.

	- Naming and tagging of images.

- Community maintained docker images like proteomics and metabolomics
  and cytometry. (Include community names L gatto, sneumann, m.jiang)

- Linux nightly build replica (bioconductor_full).

	- testing environment for users and developers/maintainers.

	- Aim is to install MOST (if not all) Bioconductor packages.

	- Better alternative than distributing specific packages in a
      image.

	- These images will be used for cloud based solutions in the near
      future like AnVIL project.

	- distributed on singularity as well.

- Improve reproducibility of Bioconductor versions and R versions
  which are closely tied together.

- Ruby and a rakefile along with a templating engine to generate all
  of our images once every 6 months. (link to src)

	- Takes away the pain of hand crafting dockerfiles each release cycl

	- recent work: improve src Dockerfiles, so that images are
      smaller. Improvements like cleaning cache etc. Not installing
      system dependencies once they have already been installed
      rocker - images.

- Docker hub allows us to build and distribute images to the
  community.

- Future:

	- Teaching workshops, and they don't have to worry about AWS
      working vs not.

	- Docker images used for distributing Bioconductor workshop
      material post conference.
